\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-05-03 paper.tex
removed array section || started lists monad section

    \section{Arrays}
    Arrays in Haskell are not treated as ordinary functions but and abstract data types.

>>>>

    \section{Lists}
    This section shows how the monadic behaviour of lists can be used in our advantage to explicitly demonstrate non-determinism. \\ \\
    In general, lists can be both \textit{deterministic} and \textit{non-deterministic}. For instance, take into consideration a list containing just one element \textbf{[27]}. Clearly, the former list is deterministic since it accommodates a single value and it is apparent that the value equals to 27. On the other hand, a list enclosing more than one element \textbf{[27, 6, 21]} introduces non-deterministic behaviour since it can have many outcomes at the same time. \\
